The Rockerverse: Packages and Applications for Containerisation with R

### 2020-03-09 rockerverse.Rmd
googleCloudRunner on CRAN

As Google Cloud Build itself can run any container, the package \pkg{googleCloudRunner} demonstrates how R can be used as the control language for one-time or batch processing jobs and scheduling of jobs\footnote{\href{https://code.markedmondson.me/googleCloudRunner/articles/cloudbuild.html}{https://code.markedmondson.me/googleCloudRunner/articles/cloudbuild.html}}.

>>>>

As Google Cloud Build itself can run any container, the package \CRANpkg{googleCloudRunner} \citep{cran:googleCloudRunner} demonstrates how R can be used as the control language for one-time or batch processing jobs and scheduling of jobs\footnote{\href{https://code.markedmondson.me/googleCloudRunner/articles/cloudbuild.html}{https://code.markedmondson.me/googleCloudRunner/articles/cloudbuild.html}}.
